---
title: "Lists - In Class Exercises"
author: "Dr. Shoemaker"
date: "DATA 2401"
output:nhtml_document

---

# Exercises: 

Make a list that contains the information on a single playing card. Suit, face, and value. 

```{r}
spades_card <- list(suit= "spade", face= "knight", value = 2)
spades_card

```


Make a second list where each element contains all the options for suit, face, and value, respectively. 

```{r}
card_options <- list(
  suit= c(1:10, "heart", "diamond", "spade"),
  face= c("jack","king", "queen"),
  value = c(1:10, 10, 10, 10)
)
card_options

```


If `Newlist <- list(a=1:10, b="Good morning", c="Hi")`, write an R statement that will add 1 to each element of the first vector in Newlist.

```{r}
Newlist <- list(a=1:10, b="Good morning", c="Hi")
Newlist[[1]]+1
Newlist
```

If `b <- list(a=1:10, c="Hello", d="AA")`, write an R expression that will give all elements of the first vector of b, except the second, and write another that returns only elements of `a` that are greater than 7.

```{r}
b <- list(a=1:10, c="Hello", d="AA") 
elements_b <- b$a[-2] #-2 removes value 2
greater_7 <- b$a[b$a > 7] #you need to make a sublist and set it in []
greater_7
```

Let `x <- list(a=5:10, c="Hello", d="AA")`, write an R statement to add a new item z = "NewItem" to the list x.

```{r}
x <- list(a=5:10, c="Hello", d="AA")
x$z = "NewItem"
x


```
